MaxEnt: What is it good for?

### 2015-06-15 ms.tex
More refs and words

\title{What is MaxEnt?}
\author{Brendon J. Brewer}

@@

@@

\section{Testable Information}

\section{A Special Case: Expected Values}\label{sec:expectations}
Refer to Jaynes here...I don't want to present all the details.

\section{Where does testable information come from?}

@@

\section{MaxEnt and Bayesian Inference}\label{sec:bayes}

\section{MaxEnt and Hierarchical Bayesian Models}
Suppose we have a discrete prior distribution $q(\xx)$. Consider some
function of the unknown quantity, $f(\xx)$.
If the value of $f(\xx)$ is known, then our distribution for $\xx$ can
be updated from $q$ to $p$ as in Section~\ref{sec:bayes}.
If we receive testable information
about the expected value of $F$, then our distribution for $\xx$ can
be updated as in Section~\ref{sec:expectations}.

@@

\bibitem[Jaynes(1979)]{stand_on_entropy} Jaynes, E. T., 1979, ``Where do we Stand on Maximum Entropy?'' in The Maximum Entropy Formalism, R. D. Levine and M. Tribus (eds.), M. I. T. Press, Cambridge, MA, p. 15
\end{thebibliography}

>>>>

\title{MaxEnt: What is it good for?}
\author{Brendon J. Brewer}

@@

The principle of maximum entropy (MaxEnt) is an idea in probability theory
that is usually associated with \citet{jaynes}. The principle may be used
to {\it assign} or {\it update} a
subjective\footnote{in the sense that the probability distribution is a model
of the state of uncertainty of an idealised rational agent, rather than
a {\it frequency distribution} such as a histogram of people's heights.}
probability distribution when you obtain a certain kind of information
called {\it testable information}. The principle is very intuitively compelling
and there are some axiomatic arguments in its favour
\citep[e.g.][]{2010arXiv1008.4831K}. However, MaxEnt has also been widely
misapplied (even by some of its staunchest defenders), misunderstood,
and poorly defended (even by Jaynes himself).

@@

\section{What is testable information?}

\section{A special case: expected values}\label{sec:expectations}
Refer to Jaynes here...I don't want to present all the details.

\section{Where is testable information in the real world?}

@@

\section{MaxEnt and Bayesian inference}\label{sec:bayes}

\section{MaxEnt and ``Hierarchical Bayesian'' models}
Suppose we have a discrete prior distribution $q(\xx)$. Consider some
function of the unknown quantity, $f(\xx)$.
If the value of $f(\xx)$ is known, then our distribution for $\xx$ can
be updated from $q$ to $p$ as in Section~\ref{sec:bayes}.
If we receive testable information
about the expected value of $F$, then our distribution for $\xx$ can
be updated as in Section~\ref{sec:expectations}.

@@

\bibitem[Jaynes(1979)]{stand_on_entropy} Jaynes, E. T., 1979, ``Where do we Stand on Maximum Entropy?'' in The Maximum Entropy Formalism, R. D. Levine and M. Tribus (eds.), M. I. T. Press, Cambridge, MA, p. 15

\bibitem[Jaynes(2003)]{jaynes} Jaynes, E. T., 2003, ``Probability Theory:
The Logic of Science'', ed. G.~Larry~Bretthorst, Cambridge University Press

\bibitem[Knuth and Skilling(2010)]{2010arXiv1008.4831K} Knuth, K.~H., 
Skilling, J.\ 2010.\ Foundations of Inference.\
Axioms 1.1 (2012): 38-73.\
ArXiv e-prints arXiv:1008.4831. 
\end{thebibliography}
